---
title: "Analysis of __DATAFILE__"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 6
  word_document: default
  md_document:
    df_print: paged
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_depth: 6
    toc_float: true
---

This is the report for the file `__DATAFILE__`.

```{r}
data <- read.csv(file = "__DATAFILE__")
```
```{r}
data$Week <- factor(
  x = as.character(data$Week),
  levels = as.character(sort(unique(data$Week))),
  ordered = TRUE
)
```


# Data Overview

The data consists of `r nrow(data)` records. There are `r length(levels(data$Member))` members. There are `r length(unique(data$Week))` weeks. A total of `r sum(data$Amount)` virtual currency was spent. A total of `r sum(data$ScrumsMissed)` scrums and `r sum(data$OtherMissed)` other meetings were missed.

## Members

The members are: `r levels(data$Member)`.


# Dollars Received

## Per User and Week

Here, we show show how much money was received per user and week.

```{r fig.height=8}
ggplot(data, aes(fill=Member, y=Amount, x=Member)) +
  geom_bar(position="stack", stat="identity") +
  geom_text(aes(label = stat(y), group = Member), stat = 'summary', fun.y = sum, hjust = 1.5) +
  facet_wrap(Week ~.) + coord_flip() +
  #scale_fill_brewer(palette = "Set3") +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  scale_fill_discrete(guide = guide_legend(nrow = 4))
```

## Per User, total

```{r}
ggplot(data, aes(fill=Member, y=Amount, x=Member, label=Amount)) +
  stat_summary(aes(x=Member, y=Amount), fun.y = sum, geom = "bar") +
  geom_text(aes(label = stat(y), group = Member), stat = 'summary', fun.y = sum, hjust = 1.5) +
  coord_flip() +
  #scale_fill_brewer(palette = "Set3") +
  theme_light() +
  theme(axis.title.y = element_blank())
```

# Per User, cumulative sum

```{r fig.height=8}
cSums <- data.frame(stringsAsFactors = FALSE)
for (member in levels(data$Member)) {
  temp <- data.frame(stringsAsFactors = FALSE)
  for (week in levels(data$Week)) {
    cSum <- data[data$Member == member & data$Week == week, ]
    temp <- rbind(temp, data.frame(
      Member = member,
      Week = week,
      Amount = sum(cSum$Amount)
    ))
  }
  temp$AmountCsum <- cumsum(temp$Amount)
  cSums <- rbind(cSums, temp)
}

ggplot(cSums, aes(x=Week, y=AmountCsum, color=Member, group = 1)) +
  scale_x_discrete() +
  geom_line() + geom_point(size = 2) +
  geom_smooth(method = "lm") + 
  theme_light() +
  theme(
    legend.position = "bottom",
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  ylab("Cumulative Sum") +
  scale_fill_discrete(guide = guide_legend(nrow = 4)) +
  #scale_color_brewer(palette = "Set3") +
  facet_wrap(Member ~., ncol = 3, scales = "fixed")
```

