---
title: "Analysis of __DATAFILE__"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 6
  word_document: default
  md_document:
    df_print: paged
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_depth: 6
    toc_float: true
---

This is the report for the file `__DATAFILE__`.

```{r warning=FALSE}
data <- read.csv(file = "__DATAFILE__", encoding = "UTF-8")
```
```{r warning=FALSE}
library(dplyr)
library(ggplot2)

data$Week <- factor(
  x = as.character(data$Week),
  levels = as.character(sort(unique(data$Week))),
  ordered = TRUE
)
```


# Data Overview

The data consists of `r nrow(data)` records. There are `r length(levels(data$Member))` members. There are `r length(unique(data$Week))` weeks.

A total of `r sum(data$Amount)` virtual currency (`r round(sum(data$Amount) / length(levels(data$Member)))` on average) was spent.

A total of `r sum(data$ScrumsMissed)` scrums and `r sum(data$OtherMissed)` other meetings were missed.

```{r}
data %>% group_by(Member) %>% summarize(S_missed = sum(ScrumsMissed), O_missed = sum(OtherMissed))
```


## Members

The members are: `r levels(data$Member)`.


# Dollars Received
In the following plots, the vertical line represents the mean.

## Per User and Week

Here, we show show how much money was received per user and week.

```{r fig.height=7}
meanAmounts <- data %>% group_by(Week) %>% summarize(mean_val = sum(Amount) / length(levels(data$Member)))

print(meanAmounts)
```


```{r fig.height=7}
ggplot(data, aes(fill=Member, y=Amount, x=Member)) +
  geom_bar(position="stack", stat="identity") +
  geom_text(aes(label = stat(y), group = Member), stat = 'summary', fun.y = sum, hjust = 1.5) +
  geom_hline(data=meanAmounts, aes(yintercept = mean_val)) +
  facet_wrap(Week ~., ncol = 3) +
  coord_flip() +
  #scale_fill_brewer(palette = "Set3") +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  scale_fill_discrete(guide = guide_legend(nrow = 5))
```

Another version, but this time we show all weeks per user:

```{r fig.height=7}
amountWeek <- data %>% group_by(Member,Week) %>% summarize(AmountSum=sum(Amount))
rangeAmountWeek <- range(amountWeek$AmountSum)

ggplot(amountWeek, aes(fill = Week, y=AmountSum, x=Week)) +
  geom_bar(stat = "identity") +
  facet_wrap(Member ~., ncol = 3, scales = "free_y") +
  #coord_flip() +
  #scale_fill_brewer(palette = "Set3") +
  theme_light() +
  theme(
    legend.position = "bottom",
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  coord_cartesian(ylim = c(rangeAmountWeek[1] - 1, rangeAmountWeek[2] + 1))

```



## Per User, total

```{r}
averageReceived <- sum(data$Amount) / length(levels(data$Member))
```

The average received per user is `r round(averageReceived, 2)`.

```{r}
ggplot(data, aes(fill=Member, y=Amount, x=Member, label=Amount)) +
  stat_summary(aes(x=Member, y=Amount), fun.y = sum, geom = "bar") +
  geom_text(aes(label = stat(y), group = Member), stat = 'summary', fun.y = sum, hjust = 1.5) +
  coord_flip() +
  #scale_fill_brewer(palette = "Set3") +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()) +
  geom_hline(yintercept = averageReceived) +
  scale_fill_discrete(guide = guide_legend(nrow = 5))
```


## Per User, cumulative sum

```{r fig.height=6}
cSums <- data.frame(stringsAsFactors = FALSE)
for (member in levels(data$Member)) {
  temp <- data.frame(stringsAsFactors = FALSE)
  for (week in levels(data$Week)) {
    cSum <- data[data$Member == member & data$Week == week, ]
    temp <- rbind(temp, data.frame(
      Member = member,
      Week = week,
      Amount = sum(cSum$Amount)
    ))
  }
  temp$AmountCsum <- cumsum(temp$Amount)
  cSums <- rbind(cSums, temp)
}

ggplot(cSums, aes(x=Week, y=AmountCsum, color=Member, group = 1)) +
  scale_x_discrete() +
  geom_line() + geom_point(size = 2) +
  geom_smooth(method = "lm") + 
  theme_light() +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  ylab("Cumulative Sum") +
  scale_fill_discrete(guide = guide_legend(nrow = 4)) +
  #scale_color_brewer(palette = "Set3") +
  facet_wrap(Member ~., ncol = 3, scales = "fixed")
```


# Scoring

We compute various scores in the range `[0,1]` based on dollars and absences. These scores are then broken down into quantiles

```{r}
dollars <- amountWeek %>% group_by(Member) %>% summarize(min = min(AmountSum), max = max(AmountSum), avg = mean(AmountSum), sum = sum(AmountSum))

# For dollars, a higher value is better. The score represents thus the
# cumulative probability to find something lower.
scoreDollarMin = ecdf(dollars$min)
dollars$minScore <- sapply(dollars$min, scoreDollarMin)
scoreDollarMax = ecdf(dollars$max)
dollars$maxScore <- sapply(dollars$max, scoreDollarMax)
scoreDollarAvg = ecdf(dollars$avg)
dollars$avgScore <- sapply(dollars$avg, scoreDollarAvg)
scoreDollarSum = ecdf(dollars$sum)
dollars$sumScore <- sapply(dollars$sum, scoreDollarSum)

# For the total score, we just add them together.
dollars$score <- (dollars$minScore + dollars$maxScore + dollars$avgScore + dollars$sumScore) / 4
```


```{r}
ggplot(data = dollars, aes(x = reorder(Member, score), y = score, color = reorder(Member, -score), fill = reorder(Member, -score))) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom") +
  scale_fill_discrete(guide = guide_legend(nrow = 5)) +
  ggtitle("Averaged scores [0,1], dollar distribution") +
  labs(fill = "Member", color = "Member")
```

Also, let's factor in the amount of missed meetings. However, these we'll compute differently. With every additionally missed meeting, the score should decrease exponentially. We calculate the score therefore as `1.05**(-n*1.2**n)`, where `n` is the number of missed meetings.

```{r}
allScores <- inner_join(dollars, data %>% group_by(Member) %>% summarize(S_missed = sum(ScrumsMissed), O_missed = sum(OtherMissed)), by = c("Member"))

allScores$S_missedScore <- sapply(allScores$S_missed, function(x) 1.05**(-x * 1.2**x))
allScores$O_missedScore <- sapply(allScores$O_missed, function(x) 1.05**(-x * 1.2**x))
allScores$scoreMiss <- allScores$S_missedScore * allScores$O_missedScore
```

The scores for absences already carry some weight, so that we can just multiply them with the dollar-scores.

```{r}
allScores$total <- allScores$score * allScores$scoreMiss
```

In the following graph, we keep the same order of members as in the previous graph, to highlight differences due to missed meetings.

```{r}
ggplot(data = allScores, aes(x = reorder(Member, score), y = total, color = reorder(Member, -score), fill = reorder(Member, -score))) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom") +
  scale_fill_discrete(guide = guide_legend(nrow = 5)) +
  ggtitle("Averaged scores [0,1], total (incl. absences)") +
  labs(fill = "Member", color = "Member")
```

## Final Ranking

There is one grade for the entire group, and each member should get a grade equal to it. According to what we presented here, each member may also receive a grade worse or better than the group. We therefore introduce 3 ranges (not quantiles, as these would split the group into 3 equally large subgroups) of the score.

```{r}
scoreStep <- (range(allScores$total)[2] - range(allScores$total)[1]) / 3
scoreRange <- c(
  min(allScores$total) + scoreStep,
  min(allScores$total) + scoreStep * 2
)

membersQ1 <- allScores %>% filter(total <= scoreRange[1])
membersQ2 <- allScores %>% filter(total > scoreRange[1] & total <= scoreRange[2])
membersQ3 <- allScores %>% filter(total > scoreRange[2])
```

The score-ranges are `x` <= `r scoreRange[1]`, `r scoreRange[1]` < `x` <= `r scoreRange[2]`, and `x` > `r scoreRange[2]`.

The `r nrow(membersQ1)` member(s) that should receive a grade __worse__ than their group are: `r paste(membersQ1$Member, collapse = ", ")`.

The `r nrow(membersQ2)` member(s) that should receive a grade __equal to__ their group are: `r paste(membersQ2$Member, collapse = ", ")`.

The `r nrow(membersQ3)` member(s) that should receive a grade __better__ than their group are: `r paste(membersQ3$Member, collapse = ", ")`.

