---
title: "Analysis of __DATAFILE__"
author: "Sebastian Hönel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
papersize: a4
urlcolor: blue
output:
  bookdown::pdf_document2:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 6
    df_print: kable
    keep_tex: yes
  md_document:
    toc: yes
    toc_depth: 6
    df_print: kable
    variant: gfm
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 6
    toc_float: yes
    df_print: kable
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

Sys.setenv(LC_ALL = "en_US.UTF-8")
Sys.setenv(LANG = "en_US.UTF-8")
```

This is the report for the file `__DATAFILE__`.

```{r warning=FALSE}
data <- read.csv(file = "__DATAFILE__", encoding = "UTF-8")

data$Member <- factor(
  x = data$Member,
  levels =sort(unique(data$Member)),
  ordered = TRUE)

data$Week <- factor(
  x = as.character(data$Week),
  levels = as.character(sort(unique(data$Week))),
  ordered = TRUE)
```
```{r warning=FALSE, message=FALSE, include=FALSE}
library(dplyr)
library(ggplot2)
```


# Data Overview

The data consists of `r nrow(data)` records. There are `r length(levels(data$Member))` members. There are `r length(unique(data$Week))` weeks.
A total of `r sum(data$Amount)` virtual currency (`r round(sum(data$Amount) / length(levels(data$Member)))` on average) was spent.
A total of `r sum(data$ScrumsMissed)` scrums and `r sum(data$OtherMissed)` other meetings were missed (table \ref{tab:members}).

```{r echo=FALSE}
knitr::kable(
  x = data %>% group_by(Member) %>% summarize("Scrums missed" = sum(ScrumsMissed), "Other meetings missed" = sum(OtherMissed)),
  booktabs = TRUE,
  caption = "All members and the number of Scrums or other meetings missed.",
  label = "members"
)
```


## Members

The members are: `r levels(data$Member)`.


# Dollars Received
In the following plots, the vertical line represents the mean.

## Per User and Week

Here, we show show how much money was received per user and week (table \ref{tab:average-dollars} and figure \ref{fig:dollars-per-week}).

```{r}
meanAmounts <- data %>% group_by(Week) %>% summarize("Average Dollars" = round(sum(Amount) / length(levels(data$Member)), 2))
```


```{r echo=FALSE}
knitr::kable(
  x = meanAmounts,
  booktabs = TRUE,
  caption = "Average amount of dollars spent/received per week and member.",
  label = "average-dollars"
)
```


```{r dollars-per-week, echo=FALSE, fig.cap="Dollars received per week and user, grouped by week.", fig.height=max(length(levels(data$Member)) * 0.75, 5)}
ggplot(data, aes(fill=Member, y=Amount, x=Member)) +
  geom_bar(position="stack", stat="identity") +
  stat_summary(aes(label = ..y.., group = Member), fun=sum, geom="text", size = 3, hjust = 1.5) +
  geom_hline(data=meanAmounts, aes(yintercept = `Average Dollars`)) +
  facet_wrap(Week ~., ncol = 3) +
  coord_flip() +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  scale_fill_discrete(guide = guide_legend(nrow = 4))
```

Another version, but this time we show all weeks per user (figure \ref{fig:dollars-per-user}):

```{r dollars-per-user, echo=FALSE, fig.cap="Dollars received per week and user, grouped by user.", fig.height=max(length(levels(data$Member)) * 0.6, 4)}
amountWeek <- data %>% group_by(Member,Week) %>% summarize(AmountSum=sum(Amount))
rangeAmountWeek <- range(amountWeek$AmountSum)

ggplot(amountWeek, aes(fill = Week, y=AmountSum, x=Week)) +
  geom_bar(stat = "identity") +
  facet_wrap(Member ~., ncol = 3, scales = "free_y") +
  #coord_flip() +
  #scale_fill_brewer(palette = "Set3") +
  theme_light() +
  theme(
    legend.position = "bottom",
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  coord_cartesian(ylim = c(rangeAmountWeek[1] - 1, rangeAmountWeek[2] + 1)) +
  scale_fill_discrete(guide = guide_legend(nrow = 1))

```



## Per User, total

Figure \ref{fig:dollars-total-per-user} shows the total amount of dollars received, per user.
Also, we show the average

```{r}
averageReceived <- sum(data$Amount) / length(levels(data$Member))
```

The average received per user is `r round(averageReceived, 2)`, and the median is `r round(median((data %>% group_by(Member) %>% summarize(bla = sum(Amount)))$bla))`.

```{r dollars-total-per-user, echo=FALSE, fig.cap="Dollars received total per user."}
ggplot(data, aes(fill=Member, y=Amount, x=Member, label=Amount)) +
  stat_summary(aes(x=Member, y=Amount), fun = sum, geom = "bar") +
  stat_summary(aes(label = ..y.., group = Member), fun=sum, geom="text", size = 5, hjust = 1.5) +
  coord_flip() +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()) +
  geom_hline(yintercept = averageReceived) +
  scale_fill_discrete(guide = guide_legend(nrow = 4))
```


## Per User, cumulative sum

Figure \ref{fig:dollars-cumulative} shows the cumulative dollars received per user and week.

```{r}
cSums <- data.frame(stringsAsFactors = FALSE)
for (member in levels(data$Member)) {
  temp <- data.frame(stringsAsFactors = FALSE)
  for (week in levels(data$Week)) {
    cSum <- data[data$Member == member & data$Week == week, ]
    temp <- rbind(temp, data.frame(
      Member = member,
      Week = week,
      Amount = sum(cSum$Amount)
    ))
  }
  temp$AmountCsum <- cumsum(temp$Amount)
  cSums <- rbind(cSums, temp)
}
```


```{r dollars-cumulative, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Cumulative dollars (per week) received per user.", fig.height=max(length(levels(data$Member)) * 0.6, 4)}
ggplot(cSums, aes(x=Week, y=AmountCsum, color=Member, group = 1)) +
  scale_x_discrete() +
  geom_line() + geom_point(size = 2) +
  geom_smooth(method = "lm", formula = y ~ x) + 
  theme_light() +
  theme(
    legend.position = "none",
    strip.background = element_rect(fill="#dfdfdf"),
    strip.text = element_text(color="black")) +
  ylab("Cumulative Sum") +
  scale_fill_discrete(guide = guide_legend(nrow = 4)) +
  #scale_color_brewer(palette = "Set3") +
  facet_wrap(Member ~., ncol = 3, scales = "fixed")
```


# Scoring

We compute various scores in the range `[0,1]` based on dollars and absences. These scores are then broken down into quantiles.
Figure \ref{fig:scores} shows the calculated scores per user.

```{r}
dollars <- amountWeek %>% group_by(Member) %>% summarize(min = min(AmountSum), max = max(AmountSum), avg = mean(AmountSum), sum = sum(AmountSum))

# For dollars, a higher value is better. The score represents thus the
# cumulative probability to find something lower.
scoreDollarMin = ecdf(dollars$min)
dollars$minScore <- sapply(dollars$min, scoreDollarMin)
scoreDollarMax = ecdf(dollars$max)
dollars$maxScore <- sapply(dollars$max, scoreDollarMax)
scoreDollarAvg = ecdf(dollars$avg)
dollars$avgScore <- sapply(dollars$avg, scoreDollarAvg)
scoreDollarSum = ecdf(dollars$sum)
dollars$sumScore <- sapply(dollars$sum, scoreDollarSum)

# For the total score, we just add them together.
dollars$score <- (dollars$minScore + dollars$maxScore + dollars$avgScore + dollars$sumScore) / 4
```


```{r scores, echo=FALSE, fig.cap="Averaged scores [0,1], dollar distribution."}
ggplot(data = dollars, aes(x = reorder(Member, score), y = score, color = reorder(Member, -score), fill = reorder(Member, -score))) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom") +
  scale_fill_discrete(guide = guide_legend(nrow = 4)) +
  labs(fill = "Member", color = "Member")
```

Also, let's factor in the amount of missed meetings. However, these we'll compute differently. With every additionally missed meeting, the score should decrease exponentially. We calculate the score therefore as `1.05**(-n*1.2**n)`, where `n` is the number of missed meetings.

```{r}
allScores <- inner_join(dollars, data %>% group_by(Member) %>% summarize(S_missed = sum(ScrumsMissed), O_missed = sum(OtherMissed)), by = c("Member"))

allScores$S_missedScore <- sapply(allScores$S_missed, function(x) 1.05**(-x * 1.2**x))
allScores$O_missedScore <- sapply(allScores$O_missed, function(x) 1.05**(-x * 1.2**x))
allScores$scoreMiss <- allScores$S_missedScore * allScores$O_missedScore
```

The scores for absences already carry some weight, so that we can just multiply them with the dollar-scores.

```{r}
allScores$total <- allScores$score * allScores$scoreMiss
```

In the following graph of figure \ref{fig:scores-incl-absences}, we keep the same order of members as in the previous graph, to highlight differences due to missed meetings.

```{r scores-incl-absences, echo=FALSE, fig.cap="Averaged scores [0,1], total (incl. absences)."}
ggplot(data = allScores, aes(x = reorder(Member, score), y = total, color = reorder(Member, -score), fill = reorder(Member, -score))) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_light() +
  theme(
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom") +
  scale_fill_discrete(guide = guide_legend(nrow = 4)) +
  labs(fill = "Member", color = "Member")
```

## Final Ranking

There is one grade for the entire group, and each member should get a grade equal to it. According to what we presented here, each member may also receive a grade worse or better than the group. We therefore introduce 3 ranges (not quantiles, as these would split the group into 3 equally large subgroups) of the score.

```{r}
scoreStep <- (range(allScores$total)[2] - range(allScores$total)[1]) / 3
scoreRange <- c(
  min(allScores$total) + scoreStep,
  min(allScores$total) + scoreStep * 2
)

membersQ1 <- allScores %>% filter(total <= scoreRange[1])
membersQ2 <- allScores %>% filter(total > scoreRange[1] & total <= scoreRange[2])
membersQ3 <- allScores %>% filter(total > scoreRange[2])
```

The score-ranges are $0\leq x\leq$ `r round(scoreRange[1], 2)`, `r round(scoreRange[1], 2)` $<x\leq$ `r round(scoreRange[2], 2)`, and  `r round(scoreRange[2], 2)` $<x\leq1$.

The `r nrow(membersQ1)` member(s) that should receive a grade __worse__ than their group are: `r paste(paste0(membersQ1$Member, " (", round(membersQ1$total, 2), ")"), collapse = ", ")`.

The `r nrow(membersQ2)` member(s) that should receive a grade __equal to__ their group are: `r paste(paste0(membersQ2$Member, " (", round(membersQ2$total, 2), ")"), collapse = ", ")`.

The `r nrow(membersQ3)` member(s) that should receive a grade __better__ than their group are: `r paste(paste0(membersQ3$Member, " (", round(membersQ3$total, 2), ")"), collapse = ", ")`.

